Output Summary

### 2021-12-11 03-post-process/output-plots.Rmd
Set up better handling of which years to plot in output RMD
An additional parameter is included that allows user to toggle on/off the inclusion of simulated years in all plots

---
title: "Output Summary"
subtitle: "Multi-Population Model"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "base"
    input: text
editor_options: 
  chunk_output_type: console
---

@@

```{r dimension-ids}
# the years included by the model
all_yrs = as.numeric(dimnames(jags_data$Pa_obs)[[1]])

# which years are "observable" for at least some quantities?
observable = (jags_data$kmax+1):jags_data$ny

>>>>

---
title: "Output Summary"
subtitle: "Multi-Population Model"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "base"
    input: text
  include_sim_years:
    label: "Include Simulated Years on Plots?"
    value: FALSE
    input: checkbox
editor_options: 
  chunk_output_type: console
---

@@

```{r dimension-ids}
# the years included by the model
all_yrs = as.numeric(dimnames(jags_data$phi_SL)[[1]])

# which years are "observable" for at least some quantities?
observable = (jags_data$kmax+1):jags_data$ny_obs

# which years are simulated for at least some quantities?
simulated = which(!(all_yrs %in% all_yrs[observable]) & all_yrs > min(all_yrs[observable]))

# which years should be included in time series plots?
if (params$include_sim_years) {
  ts_yrs = c(observable, simulated)
} else {
  ts_yrs = observable
}

# which years can be plotted for SARs? Drop off last kmax years
# since brood year adult returns not complete
sar_yrs = ts_yrs[-((length(ts_yrs) - jags_data$kmax + 1):length(ts_yrs))]
